### 2015-09-21 stuff/dirfields/DirFields.tex
...

%surface (manifold) -> M, S, \Omega 
\newcommand{\M}{M}
%volume element (volume measure) -> \mu, dA, d\Omega
\newcommand{\dA}{dA}
%director field (contra-vector)
\newcommand{\p}{\mathbf{p}}
\newcommand{\q}{\mathbf{q}}
%director field (co-vector, flat of contra-vector)
\newcommand{\pfl}{\mathbf{p}^{\flat}}
\newcommand{\qfl}{\mathbf{q}^{\flat}}
%discrete director field (co-vector, flat of contra-vector)
\newcommand{\pflh}{\mathbf{p}^{\flat}_{h}}
\newcommand{\pflhOld}{\widehat{\mathbf{p}}^{\flat}_{h}}
\newcommand{\qflh}{\mathbf{q}^{\flat}_{h}}
%discrete director field (contra-vector)
\newcommand{\ph}{\mathbf{p}_{h}}
%discrete PD director field (co-vector, flat of contra-vector)
\newcommand{\PDpflh}{\underline{\mathbf{p}}^{\flat}_{h}}
\newcommand{\PDqflh}{\underline{\mathbf{q}}^{\flat}_{h}}
%discrete director field (contra-vector)
\newcommand{\PDph}{\underline{\mathbf{p}}_{h}}
%discrete PD director field OLD SOLUTION (co-vector, flat of contra-vector)
\newcommand{\PDpflhOld}{\underline{\widehat{\mathbf{p}}}^{\flat}_{h}}
%Frank Oseen Energy (without Lagrange term for normalizing)
\newcommand{\EOS}{E_{\text{OS}}}
%Normalizing energy
\newcommand{\EN}{E_{n}}
%Laplace-Beltrami or Rot-Rot-Laplace
\newcommand{\LB}{\Delta^{\text{\tiny RR}}}
%Laplace-CoBeltrami or Grad-Div-Laplace
\newcommand{\LCB}{\Delta^{\text{\tiny GD}}}
%Laplace-deRham
\newcommand{\LDR}{\Delta^{\text{\tiny dR}}}
%discrete Laplace-Beltrami or Rot-Rot-Laplace
\newcommand{\LBh}{\LB_{h}}
%Laplace-CoBeltrami or Grad-Div-Laplace
\newcommand{\LCBh}{\LCB_{h}}
%Laplace-deRham
\newcommand{\LDRh}{\LDR_{h}}
%Landau symbol
\renewcommand{\O}{\mathcal{O}}
%Vertices
\newcommand{\V}{\mathcal{V}}
%Edges
\newcommand{\E}{\mathcal{E}}
%Faces
\newcommand{\F}{\mathcal{F}}
%edge vector
\newcommand{\e}{\mathbf{e}}
%vertex vector
\renewcommand{\v}{\mathbf{v}}

@@

  With the  \( L^{2} \)-orthogonality of the exterior derivative and coderivative and a arbitrary \( \alpha\in\Lambda^{1}(M) \) we get
  \begin{align}
    \int_{\M} \left\langle\frac{\delta\EOS}{\delta\pfl} , \alpha \right\rangle \dA
      &= \lim_{\epsilon\rightarrow 0} \frac{1}{\epsilon}\left( \EOS\left[ \pfl + \epsilon\alpha \right] - \EOS\left[ \pfl\right]\right) \\
      &=  \lim_{\epsilon\rightarrow 0} \frac{1}{2\epsilon} \int_{\M} 
                K_{1}\left( 2\epsilon \left( \excod\pfl \right)\left( \excod\alpha \right) 
                            + \epsilon^{2}\left( \excod\alpha \right)^{2} \right) \\
      &\phantom{= \lim_{\epsilon\rightarrow 0} \frac{1}{2\epsilon} \int_{\M}}
                +K_{3}\left(2\epsilon\left\langle \exd\pfl, \exd\alpha \right\rangle
                            + \epsilon^{2}\left\| \exd\alpha \right\|^{2}\right)\dA \\
      &= -\int_{\M} K_{1} \left\langle \LCB\pfl, \alpha \right\rangle + K_{3} \left\langle \LB\pfl, \alpha \right\rangle \dA \\
      &= \int_{\M} \left\langle -\left( K_{1}\LCB + K_{3}\LB\right)\pfl , \alpha \right\rangle \dA
  \end{align}
  where \( \LB = -\excod\exd = *\exd *\exd  \) is the Vector-Laplace-Beltrami-Operator or Rot-Rot-Laplace 
  and \( \LCB = - \exd\excod = \exd * \exd * \) is the Vector-Laplace-CoBeltrami-Operator or Grad-Div-Laplace.
  Hence, for a One-Constant-Approximation \( K_{1} = K_{3} =: K_{0} \), we obtain
  \begin{align}
    \int_{\M} \left\langle\frac{\delta\EOS}{\delta\pfl} , \alpha \right\rangle \dA
     &= \int_{\M} \left\langle K_{0}\LDR\pfl , \alpha \right\rangle \dA
  \end{align}
  where \( \LDR = -\LB - \LCB = \excod\exd + \exd\excod\) is the Laplace-de Rham operator.

@@

    In the discrete exterior calculus discrete Operators are defined by successively interpretation of the basic operations on the forms, 
    like the Hodge operator \( * \) or the exterior derivative \( \exd \), as geometric operators on the simplices, 
    like the Voronoi dual operator \( \star \) or the boundary operator \( \partial \) (see \cite{hirani}).
    This results for example to a discrete definition of \( \LB \) for a discrete 1-form \( \pflh\in\Lambda^{1}_{h}(M) \) on a edge 
    \(e\in\E \)
    \begin{align}
      \LBh\pflh(e) &:=  \left(*\exd*\exd \pflh\right)(e)
                     = -\frac{\left| e \right|}{\left| \star e \right|} \left(\exd * \exd  \pflh\right)(\star e) \\
                    &=  -\frac{\left| e \right|}{\left| \star e \right|} \left(* \exd  \pflh\right)(\partial\star e)
                     = -\frac{\left| e \right|}{\left| \star e \right|} \sum_{f\succ e} s_{f,e} \left(* \exd \pflh\right) (\star f) \\
                    &= -\frac{\left| e \right|}{\left| \star e \right|} \sum_{f\succ e} \frac{s_{f,e}}{\left| f \right|} 
                                \left(\exd\pflh\right)(f)
                     = -\frac{\left| e \right|}{\left| \star e \right|} \sum_{f\succ e} \frac{s_{f,e}}{\left| f \right|} \pflh(\partial f)\\
                    &= -\frac{\left| e \right|}{\left| \star e \right|} \sum_{f\succ e} \frac{s_{f,e}}{\left| f \right|}
                                \sum_{\tilde{e}\prec f} s_{f,\tilde{e}} \pflh(\tilde{e})
    \end{align}
    or for \( \LCB \)
    \begin{align}
      \LCBh\pflh(e) &:= \left( \exd * \exd * \pflh\right) (e)
                      = \left( * \exd *\pflh \right) (\partial e) \\
                     &= \sum_{v\prec e} s_{v,e} \left( * \exd * \pflh \right)(v) 
                      = \sum_{v\prec e} \frac{s_{v,e}}{\left| \star v \right|} \left( \exd * \pflh \right)(\star v)\\
                     &= \sum_{v\prec e} \frac{s_{v,e}}{\left| \star v \right|} \left( * \pflh \right)(\partial\star v)
                      = -\sum_{v\prec e} \frac{s_{v,e}}{\left| \star v \right|} \sum_{\tilde{e}\succ v}
                                s_{v,\tilde{e}} \left( * \pflh \right) (\star \tilde{e}) \\
                     &= -\sum_{v\prec e} \frac{s_{v,e}}{\left| \star v \right|} \sum_{\tilde{e}\succ v}
                                s_{v,\tilde{e}} \frac{\left| \star\tilde{e} \right|}{\left| \tilde{e} \right|}\pflh(\tilde{e})
    \end{align}
    where the sign \( s_{f,e} \) is +1 if the face \( f\succ e \) is in the left of the edge \( e \) (-1 otherwise)
    and \( s_{v,e} \) is +1 if the edge \( e\succ v \) points to the vertex \( v \) and -1 if \( e \) points away from \( v \).
    We see \( \LBh \), \( \LCBh \) and also \( \LDRh := -\LBh -\LCBh \) are linear operators in \( \pflh(\tilde{e}) \)
    and therefor results in sparse matrices if the \( \pflh(\tilde{e}) \) are our degree of freedoms.
    ...explainable figures...

@@

    The basis for contravariant vectors at \( c(e) \) is composed of
    \begin{align}
      \partial_{e}X &:= \e = \v_{2} - \v_{1} \\
      \partial_{\star e}X &:= *\e =  c(f_{2}) - c(f_{1})
    \end{align}
    if \( e=\left[ v_{1}, v_{2} \right] \) and the face \( f_{1} \) lay right and \( f_{2} \) left of \( e \) (...figure...). 
    This definitions are consistent with the canonical basis, if the position \( X \) is a barycentric parametrisation of the edge \( e \)
    resp. its dual, i.e. for
    \begin{align}
      X_{e}(t_{e}) &= t_{e}\v_{2} + \left( 1 - t_{e} \right)\v_{2} \text{ for } t\in[0,1]\\
      X_{\star e}(t_{\star e}) &=\begin{cases}
                        2t_{\star e}c(e) + \left( 1 - 2t_{\star e} \right) c(f_{1}) & \text{if } t_{\star e}\in\left[ 0 , \frac{1}{2} \right] \\
                        \left(1 - t_{\star e}\right) c(e) + \left( 2t_{\star e} - 1 \right) c(f_{1}) 
                                & \text{if } t_{\star e}\in \left[\frac{1}{2} , 1\right]
                      \end{cases}
    \end{align}
    holds \( \partial_{e}X = \partial_{t_{e}}X_{e} \) 
    and \( \partial_{\star e}X = \frac{1}{2} \left( \partial_{t_{\star e}}X_{\star e}|_{\left[ 0 , \frac{1}{2} \right]} 
                                                   + \partial_{t_{\star e}}X_{\star e}|_{\left[\frac{1}{2}, 1 \right]}\right) \).
    Therefore we get the local metric tensor
    \begin{align}
      \mathbf{g}_h(e) &= \left| e \right|^{2} \left( dx^{e} \right)^{2} + \left| \star e \right|^{2} \left( dx^{\star e} \right)^{2}
    \end{align}
    where \( \left\{  dx^{e}, dx^{\star e} \right\} \) are the dual base of \( \left\{ \partial_{e}X, \partial_{\star e}X \right\} \),
    i.e. \( dx^{i}\left(\partial_{j}X\right) = \delta^{i}_{j} \) for \( i,j\in\left\{ e, \star e \right\} \).
    This gives us the great possibility to define
    \begin{align}
      \PDpflh(e) &:= 
                   \begin{bmatrix}
                     \pflh \\ *\pflh 
                   \end{bmatrix}_{\text{PD}} (e)
                   := \pflh(e)dx^{e} + \pflh(\star e)  dx^{\star e} \\
                   &= \pflh(e)dx^{e} - \frac{\left| \star e \right|}{\left| e \right|} \left(*\pflh\right)(e)  dx^{\star e} \\
      \PDph(e) &:= \left(\PDpflh(e)\right)^{\sharp} 
                 = \frac{1}{\left| e \right|^{2}} \pflh(e)\partial_{e}X + \frac{1}{\left|\star e \right|^{2}} \pflh(\star e)\partial_{\star e}X \\
               & =  \frac{1}{\left| e \right|} \left( \frac{1}{\left| e \right|} \pflh(e)\partial_{e}X 
                                                     -\frac{1}{\left|\star e \right|} \left(*\pflh\right)(e) \partial_{\star e}X\right)
    \end{align}
    We call \( \PDpflh(e) \) the discrete Primal-Dual-1-form (short PD-1-form) and \( \PDph \) the discrete Primal-Dual-vector field
    (short PD-vector field).
    Hence, we get for the square of the norm on \( c(e) \) by contract the PD-1-Form with its corresponding PD-Vector
    \begin{align}
      \left\| \PDpflh \right\|_{h}^{2}(e) := \left( \PDpflh\left( \PDph \right) \right)(e)
                                       = \frac{1}{\left| e \right|^{2}}\left( \left[ \pflh(e) \right]^{2} 
                                                                             +\left[ \left(*\pflh\right)(e) \right]^{2}\right)
    \end{align}
    In general, we also get a local discrete inner product between \( \PDpflh \) and another PD-1-form \( \PDqflh \) by
    \begin{align}
      \left\langle \PDqflh , \PDpflh \right\rangle_{h}(e)
          &:= \left( \PDqflh\left( \PDph \right) \right)(e)
                                       = \frac{1}{\left| e \right|^{2}}\left( \left[\pflh\qflh\right](e) 
                                                                             +\left[\left(*\pflh\right)\left(*\qflh\right)\right](e) \right)
    \end{align}

@@

              \left( *\pflhOld \right)^{2} & \pflhOld\left( *\pflhOld  \right) \\
              \pflhOld\left( *\pflhOld  \right) & \left( \pflhOld \right)^{2}
            \end{bmatrix} \cdot \PDpflh
        =: \left( \PDpflhOld \otimes_{h} \PDpflhOld \right)^{\sharp,\cdot} \cdot \PDpflh

@@

    with a formally defined local outer product \( \otimes_{h} \) for PD-1-forms,
    which respect the discrete local metric.

    With the Taylor linearization and the implicit Euler scheme, we have to solve in every time steps and all \( e\in\E \)
    \begin{align}
      \left[ \frac{1}{\tau} + K_{0}\LDRh + K_{n}\left( \left\| \PDpflhOld \right\|_{h}^{2} - 1 \right) \right]\PDpflh
          + 2K_{n} \left( \PDpflhOld \otimes_{h} \PDpflhOld \right) \cdot \PDpflh
          &= \left[\frac{1}{\tau} + 2K_{n}\left\| \PDpflhOld \right\|_{h}^{2}\right]\PDpflhOld
    \end{align}
    resp.
    %\resizebox{0.9\textwidth}{!}{\begin{minipage}{\linewidth}
    \begin{align} 
      \left[ \frac{1}{\tau}
          - \begin{bmatrix}
               K_{1} \\ K_{3}
            \end{bmatrix} \LCBh
            -\begin{bmatrix}
               K_{3} \\ K_{1}
            \end{bmatrix} \LBh
          + K_{n}\left( \left\| \PDpflhOld \right\|_{h}^{2} - 1 \right) \right]\PDpflh
          + 2K_{n} \left( \PDpflhOld \otimes_{h} \PDpflhOld \right) \cdot \PDpflh
          &= \left[\frac{1}{\tau} + 2K_{n}\left\| \PDpflhOld \right\|_{h}^{2}\right]\PDpflhOld
    \end{align}
    %\end{minipage}}

>>>>

%surface (manifold) -> M, S, \Omega 
\newcommand{\M}{M}
%volume element (volume measure) -> \mu, dA, d\Omega
\newcommand{\dA}{dA}
%director field (contra-vector)
\newcommand{\p}{\mathbf{p}}
\newcommand{\q}{\mathbf{q}}
%director field (co-vector, flat of contra-vector)
\newcommand{\pfl}{\mathbf{p}^{\flat}}
\newcommand{\qfl}{\mathbf{q}^{\flat}}
%discrete director field (co-vector, flat of contra-vector)
\newcommand{\pflh}{\mathbf{p}^{\flat}_{h}}
\newcommand{\pflhOld}{\widehat{\mathbf{p}}^{\flat}_{h}}
\newcommand{\qflh}{\mathbf{q}^{\flat}_{h}}
%discrete director field (contra-vector)
\newcommand{\ph}{\mathbf{p}_{h}}
%discrete PD director field (co-vector, flat of contra-vector)
\newcommand{\PDpflh}{\underline{\mathbf{p}}^{\flat}_{h}}
\newcommand{\PDqflh}{\underline{\mathbf{q}}^{\flat}_{h}}
%discrete director field (contra-vector)
\newcommand{\PDph}{\underline{\mathbf{p}}_{h}}
\newcommand{\PDqh}{\underline{\mathbf{q}}_{h}}
%discrete PD director field OLD SOLUTION (co-vector, flat of contra-vector)
\newcommand{\PDpflhOld}{\underline{\widehat{\mathbf{p}}}^{\flat}_{h}}
%discrete director field OLD SOLUTION (contra-vector)
\newcommand{\PDphOld}{\underline{\widehat{\mathbf{p}}}_{h}}
%Frank Oseen Energy (without Lagrange term for normalizing)
\newcommand{\EOS}{E_{\text{FO}}}
%Normalizing energy
\newcommand{\EN}{E_{n}}
%Laplace-Beltrami or Rot-Rot-Laplace
\newcommand{\LB}{\boldsymbol{\Delta}^{\text{\tiny RR}}}
%Laplace-CoBeltrami or Grad-Div-Laplace
\newcommand{\LCB}{\boldsymbol{\Delta}^{\text{\tiny GD}}}
%Laplace-deRham
\newcommand{\LDR}{\boldsymbol{\Delta}^{\text{\tiny dR}}}
%discrete Laplace-Beltrami or Rot-Rot-Laplace
\newcommand{\LBh}{\LB_{h}}
%Laplace-CoBeltrami or Grad-Div-Laplace
\newcommand{\LCBh}{\LCB_{h}}
%Laplace-deRham
\newcommand{\LDRh}{\LDR_{h}}
%Landau symbol
\renewcommand{\O}{\mathcal{O}}
%Vertices
\newcommand{\V}{\mathcal{V}}
%Edges
\newcommand{\E}{\mathcal{E}}
%Faces
\newcommand{\F}{\mathcal{F}}
%edge vector
\newcommand{\e}{\mathbf{e}}
%vertex vector
\renewcommand{\v}{\mathbf{v}}
%PD-Basis
\newcommand{\PDxi}{\boldsymbol{\xi}}

@@

  With the  \( L^{2} \)-orthogonality of the exterior derivative and coderivative 
  (\( \left\langle \exd\bullet, \bullet  \right\rangle_{L^{2}} = \left\langle \bullet,\excod\bullet \right\rangle_{L^{2}} \))
  and a arbitrary \( \alpha\in\Lambda^{1}(M) \) we get
  \begin{align}
    \int_{\M} \left\langle\frac{\delta\EOS}{\delta\pfl} , \alpha \right\rangle \dA
      &= \lim_{\epsilon\rightarrow 0} \frac{1}{\epsilon}\left( \EOS\left[ \pfl + \epsilon\alpha \right] - \EOS\left[ \pfl\right]\right) \\
      &=  \lim_{\epsilon\rightarrow 0} \frac{1}{2\epsilon} \int_{\M} 
                K_{1}\left( 2\epsilon \left( \excod\pfl \right)\left( \excod\alpha \right) 
                            + \epsilon^{2}\left( \excod\alpha \right)^{2} \right) \\
      &\phantom{= \lim_{\epsilon\rightarrow 0} \frac{1}{2\epsilon} \int_{\M}}
                +K_{3}\left(2\epsilon\left\langle \exd\pfl, \exd\alpha \right\rangle
                            + \epsilon^{2}\left\| \exd\alpha \right\|^{2}\right)\dA \\
      &= -\int_{\M} K_{1} \left\langle \LCB\pfl, \alpha \right\rangle + K_{3} \left\langle \LB\pfl, \alpha \right\rangle \dA \\
      &= \int_{\M} \left\langle -\left( K_{1}\LCB + K_{3}\LB\right)\pfl , \alpha \right\rangle \dA
  \end{align}
  where \( \LB = -\excod\exd = *\exd *\exd  \) is the Vector-Laplace-Beltrami-Operator or Rot-Rot-Laplace 
  and \( \LCB = - \exd\excod = \exd * \exd * \) is the Vector-Laplace-CoBeltrami-Operator or Grad-Div-Laplace.
  Hence, for a One-Constant-Approximation \( K_{1} = K_{3} =: K_{0} \), we obtain
  \begin{align}
    \int_{\M} \left\langle\frac{\delta\EOS}{\delta\pfl} , \alpha \right\rangle \dA
     &= \int_{\M} \left\langle K_{0}\LDR\pfl , \alpha \right\rangle \dA
  \end{align}
  where \( \LDR = -\LB - \LCB = \excod\exd + \exd\excod\) is the Laplace-de Rham operator.

@@

    In the discrete exterior calculus discrete Operators are defined by successively interpretation of the basic operations on the forms, 
    like the Hodge operator \( * \) or the exterior derivative \( \exd \), as geometric operators on the simplices, 
    like the Voronoi dual operator \( \star \) or the boundary operator \( \partial \) (see \cite{hirani}).
    This results for example to a discrete definition of \( \LB \) for a discrete 1-form \( \pflh\in\Lambda^{1}_{h}(M) \) on a edge 
    \(e\in\E \)
      \LBh\pflh(e) &:=  \left(*\exd*\exd \pflh\right)(e)
                     = -\frac{\left| e \right|}{\left| \star e \right|} \left(\exd * \exd  \pflh\right)(\star e) \\
                    &=  -\frac{\left| e \right|}{\left| \star e \right|} \left(* \exd  \pflh\right)(\partial\star e)
                     = -\frac{\left| e \right|}{\left| \star e \right|} \sum_{f\succ e} s_{f,e} \left(* \exd \pflh\right) (\star f) \\
                    &= -\frac{\left| e \right|}{\left| \star e \right|} \sum_{f\succ e} \frac{s_{f,e}}{\left| f \right|} 
                                \left(\exd\pflh\right)(f)
                     = -\frac{\left| e \right|}{\left| \star e \right|} \sum_{f\succ e} \frac{s_{f,e}}{\left| f \right|} \pflh(\partial f)\\
                    &= -\frac{\left| e \right|}{\left| \star e \right|} \sum_{f\succ e} \frac{s_{f,e}}{\left| f \right|}
                                \sum_{\tilde{e}\prec f} s_{f,\tilde{e}} \pflh(\tilde{e})
    or for \( \LCB \)
      \LCBh\pflh(e) &:= \left( \exd * \exd * \pflh\right) (e)
                      = \left( * \exd *\pflh \right) (\partial e) \\
                     &= \sum_{v\prec e} s_{v,e} \left( * \exd * \pflh \right)(v) 
                      = \sum_{v\prec e} \frac{s_{v,e}}{\left| \star v \right|} \left( \exd * \pflh \right)(\star v)\\
                     &= \sum_{v\prec e} \frac{s_{v,e}}{\left| \star v \right|} \left( * \pflh \right)(\partial\star v)
                      = -\sum_{v\prec e} \frac{s_{v,e}}{\left| \star v \right|} \sum_{\tilde{e}\succ v}
                                s_{v,\tilde{e}} \left( * \pflh \right) (\star \tilde{e}) \\
                     &= -\sum_{v\prec e} \frac{s_{v,e}}{\left| \star v \right|} \sum_{\tilde{e}\succ v}
                                s_{v,\tilde{e}} \frac{\left| \star\tilde{e} \right|}{\left| \tilde{e} \right|}\pflh(\tilde{e})
    where the sign \( s_{f,e} \) is +1 if the face \( f\succ e \) is in the left of the edge \( e \) (-1 otherwise)
    and \( s_{v,e} \) is +1 if the edge \( e\succ v \) points to the vertex \( v \) and -1 if \( e \) points away from \( v \)
    (see figure \ref{figSigns}).
    We see \( \LBh \), \( \LCBh \) and also \( \LDRh := -\LBh -\LCBh \) are linear operators in \( \pflh(\tilde{e}) \)
    and therefor results in sparse matrices if the \( \pflh(\tilde{e}) \) are our degree of freedoms.
    \begin{figure}
      \begin{minipage}[htp]{.25\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{bilder/tikz/LBDEC.pdf}
      \end{minipage}\hfill
      \begin{minipage}[htp]{.7\textwidth}
        \centering
        \includegraphics[width=.9\textwidth]{bilder/tikz/LCBDEC.pdf}
      \end{minipage}
      \caption{Signs \( s \) on example mesh extracts, which affected the discretization of the discrete Laplace operators.
               Left (\( \LBh \)): The edge of interest \( e \) is the middle edge.
                                  The bold signs in the middle of the faces indicate \( s_{f,e} \).
                                  The other signs at the local edges \( \tilde{e} \) (regarding the two faces \( f \)) indicate \( s_{f,\tilde{e}} \).
               Right (\( \LCBh \)): The edge of interest \( e \) is also the middle edge.
                                    The bold signs above the two inner vertices \( v \) indicate \( s_{v,e} \).
                                    The other signs at the local edges \( \tilde{e} \) (regarding the two vertices \( v \))
                                    indicate \( s_{v,\tilde{e}} \).}
       \label{figSigns}
    \end{figure}

@@

    The basis for contravariant vectors at \( c(e) \) is composed of
      \partial_{e}X &:= \e = \v_{2} - \v_{1} \\
      \partial_{\star e}X &:= *\e =  c(f_{2}) - c(f_{1})
    if \( e=\left[ v_{1}, v_{2} \right] \) and the face \( f_{1} \) lay right and \( f_{2} \) left of \( e \) (...figure...). 
    This definitions are consistent with the canonical basis, if the position \( X \) is a barycentric parametrisation of the edge \( e \)
    resp. its dual, i.e. for
      X_{e}(t_{e}) &= t_{e}\v_{2} + \left( 1 - t_{e} \right)\v_{2} \text{ for } t\in[0,1]\\
      X_{\star e}(t_{\star e}) &=\begin{cases}
                        2t_{\star e}c(e) + \left( 1 - 2t_{\star e} \right) c(f_{1}) & \text{if } t_{\star e}\in\left[ 0 , \frac{1}{2} \right] \\
                        \left(1 - t_{\star e}\right) c(e) + \left( 2t_{\star e} - 1 \right) c(f_{1}) 
                                & \text{if } t_{\star e}\in \left[\frac{1}{2} , 1\right]
                      \end{cases}
    holds \( \partial_{e}X = \partial_{t_{e}}X_{e} \) 
    and \( \partial_{\star e}X = \frac{1}{2} \left( \partial_{t_{\star e}}X_{\star e}|_{\left[ 0 , \frac{1}{2} \right]} 
                                                   + \partial_{t_{\star e}}X_{\star e}|_{\left[\frac{1}{2}, 1 \right]}\right) \).
    Therefore we get the local metric tensor
      \mathbf{g}_h(e) &= \left| e \right|^{2} \left( dx^{e} \right)^{2} + \left| \star e \right|^{2} \left( dx^{\star e} \right)^{2}
    where \( \left\{  dx^{e}, dx^{\star e} \right\} \) are the dual base of \( \left\{ \partial_{e}X, \partial_{\star e}X \right\} \),
    i.e. \( dx^{i}\left(\partial_{j}X\right) = \delta^{i}_{j} \) for \( i,j\in\left\{ e, \star e \right\} \).
    This gives us the great possibility to define
      \PDpflh(e) &:= \pflh(e)dx^{e} + \pflh(\star e)  dx^{\star e} 
                   = \pflh(e)dx^{e} - \frac{\left| \star e \right|}{\left| e \right|} \left(*\pflh\right)(e)  dx^{\star e} \\
                 &=  \pflh(e)\PDxi^{e} + \left(*\pflh\right)(e)\PDxi^{\star e}
                 =:
                   \end{bmatrix}_{\text{PD}} (e)
    where \( \PDxi^{e}:=dx^{e} \) and \( \PDxi^{\star e}:= - \frac{\left| \star e \right|}{\left| e \right|}dx^{\star e}\) are the
    contravariant Primal-Dual-basis (PD-basis), which we want to use.
    \( \PDpflh(e) \) is called the discrete Primal-Dual-1-form (PD-1-form).
    With this scaling and the condition \( \PDxi_{i}(\PDxi^{j}) = \delta^{j}_{i} \), 
    it is also possible to define the covariant PD-basis as 
    \( \PDxi_{e}:=\partial_{e}X \) and \( \PDxi_{\star e}:= -\frac{\left| e \right|}{\left| \star e \right|}\partial_{\star e}X \).
    Hence, we obtain for the discrete Primal-Dual-vector field (PD-vector field) \( \PDph \)
      \PDph(e) &:= \left(\PDpflh(e)\right)^{\sharp} 
                 = \frac{1}{\left| e \right|^{2}} \pflh(e)\partial_{e}X + \frac{1}{\left|\star e \right|^{2}} \pflh(\star e)\partial_{\star e}X \\
               &= \frac{1}{\left| e \right|^{2}} \pflh(e)\partial_{e}X 
                   -\frac{1}{\left| e \right|\left|\star e \right|} \left(*\pflh\right)(e) \partial_{\star e}X \\
               &= \frac{1}{\left| e \right|^{2}}\left[ \pflh(e)\PDxi_{e} + \left(*\pflh\right)(e)\PDxi_{\star e} \right]
               =: \begin{bmatrix}
                   \end{bmatrix}^{\text{PD}} (e)
    Hence, we get for the square of the norm on \( c(e) \) 
    (and also with a constant interpolation on the whole edge) by contract the PD-1-Form with its corresponding PD-Vector
      \left\| \PDpflh \right\|_{h}^{2}(e) := \left( \PDpflh\left( \PDph \right) \right)(e)
                                       = \frac{1}{\left| e \right|^{2}}\left( \left[ \pflh(e) \right]^{2} 
                                                                             +\left[ \left(*\pflh\right)(e) \right]^{2}\right)
    In general, we also get a local discrete inner product between \( \PDpflh \) and another PD-1-form \( \PDqflh \) by
      \left\langle \PDqflh , \PDpflh \right\rangle_{h}(e)
          &:= \left( \PDqflh\left( \PDph \right) \right)(e)
                                       = \frac{1}{\left| e \right|^{2}}\left( \left[\pflh\qflh\right](e) 
                                                                             +\left[\left(*\pflh\right)\left(*\qflh\right)\right](e) \right)
    or a outer product between the PD-1-form \( \PDpflh \) and the PD-vector  \( \PDqh \) to produce the PD-(1,1)-Tensor
      \left(\PDpflh \otimes \PDqh\right) 
          &:= \frac{1}{\left| e \right|^{2}} \left( \pflh\qflh \PDxi^{e}\otimes\PDxi_{e} 
                                                   +\pflh(*\qflh) \PDxi^{e}\otimes\PDxi_{\star e}
                                                   +(*\pflh)\qflh \PDxi^{\star e}\otimes\PDxi_{e}
                                                   +(*\pflh)(*\qflh)\PDxi^{\star e}\otimes\PDxi_{\star e}\right)\\
          &=: \frac{1}{\left| e \right|^{2}} 
              \pflh\qflh & \pflh(*\qflh) \\
              (*\pflh)\qflh & (*\pflh)(*\qflh)
            \end{bmatrix}^{D}_{P} 
    (Arguments \( (e) \) are omitted)

@@

              \left( \pflhOld \right)^{2} & \pflhOld\left( *\pflhOld  \right) \\
              \pflhOld\left( *\pflhOld  \right) & \left( * \pflhOld \right)^{2}
            \end{bmatrix}_{P}^{D} \cdot \PDpflh
        = \left( \PDpflhOld \otimes \PDphOld \right) \cdot \PDpflh

@@

    With the Taylor linearization and the implicit Euler scheme, we have to solve the following PD-DEC-Problem in every time steps and all \( e\in\E \)
    \begin{align}
      \left[ \frac{1}{\tau} + K_{0}\LDRh + K_{n}\left( \left\| \PDpflhOld \right\|_{h}^{2} - 1 \right) \right]\PDpflh
          + 2K_{n} \left( \PDpflhOld \otimes \PDphOld \right) \cdot \PDpflh
          &= \left[\frac{1}{\tau} + 2K_{n}\left\| \PDpflhOld \right\|_{h}^{2}\right]\PDpflhOld
    \end{align}
    resp.
    %\resizebox{0.9\textwidth}{!}{\begin{minipage}{\linewidth}
    \begin{align} 
      \left[ \frac{1}{\tau}
          - \begin{bmatrix}
               K_{1} \\ K_{3}
            \end{bmatrix} \LCBh
            -\begin{bmatrix}
               K_{3} \\ K_{1}
            \end{bmatrix} \LBh
          + K_{n}\left( \left\| \PDpflhOld \right\|_{h}^{2} - 1 \right) \right]\PDpflh
          + 2K_{n} \left( \PDpflhOld \otimes \PDphOld \right) \cdot \PDpflh
          &= \left[\frac{1}{\tau} + 2K_{n}\left\| \PDpflhOld \right\|_{h}^{2}\right]\PDpflhOld
    \end{align}
    %\end{minipage}}

\section{Notes on Implementation}

  \subsection{Edge mesh}

    \subsubsection{Iterators}

  \subsection{Matrix assembling}

  \subsection{Sharp and flat interpolations}
